---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
Read the "activity" datapack

```{r read csv, echo=TRUE}
activity <- read.csv("activity.csv",header=TRUE)
```

Format second columns as Date
```{r format date, echo=TRUE}
factortocharacter <- as.character(activity[,2])
activity[,2] <- as.Date(factortocharacter,format="%Y-%m-%d")
```



## What is mean total number of steps taken per day?


Table of the total number of steps taken per day
```{r total steps per day, echo=TRUE}
totalsteps <- aggregate(activity$steps, by=list(Date=activity$date), FUN=sum)
```

Histogram of the total number of steps taken each day

```{r histogram of total steps, echo=TRUE}
hist(totalsteps$x, breaks = 6, main = "Frequency of number of steps per day", 
    xlab = "Number of steps per day", ylab = "Frequency", col = "red")
```

```{r mean total steps per day, echo=TRUE}
mean(totalsteps$x,na.rm=TRUE)
```

```{r median total steps per day, echo=TRUE}
median(totalsteps$x,na.rm=TRUE)
```


## What is the average daily activity pattern?


Make a time series plot (i.e. ðšðš¢ðš™ðšŽ = "ðš•") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r average steps by interval, echo=TRUE}
averagestepstime <- aggregate(activity$steps,by=list(Interval=activity$interval),FUN=mean,na.rm=TRUE)
plot(averagestepstime,type="l",xlab="Time",ylab="Average Number of steps")
```

Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r interval max for average steps , echo=TRUE}
maxsteps <- max(averagestepstime$x)
averagestepstime$Interval[averagestepstime$x==maxsteps]
```

The interval from 8:35 to 8:40


## Imputing missing values


Number of NA value in activity datafram
```{r number of na , echo=TRUE}
sum(is.na(activity$steps))
```


## Are there differences in activity patterns between weekdays and weekends?
